### 2024-10-17 base-rates.qmd
20241016 - figure alt text

::: {#fig-probabilityNomogram}
![](images/probabilityNomogram.png){width=50%}\

@@

::: {#fig-probabilityNomogramLine}
![](images/probabilityNomogramLine.png){width=50%}\

>>>>

::: {#fig-probabilityNomogram}
![](images/probabilityNomogram.png){width=50% fig-alt="Probability Nomogram. (Figure retrieved from https://upload.wikimedia.org/wikipedia/commons/thumb/6/66/Fagan_nomogram.svg/945px-Fagan_nomogram.svg.png)"}

@@

::: {#fig-probabilityNomogramLine}
![](images/probabilityNomogramLine.png){width=50% fig-alt="Probability Nomogram. (Figure retrieved from https://upload.wikimedia.org/wikipedia/commons/thumb/6/66/Fagan_nomogram.svg/945px-Fagan_nomogram.svg.png). Also provided in: @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

### 2024-10-17 basic-statistics.qmd
20241016 - figure alt text

::: {#fig-nhstConfusionMatrix}
![](images/nhstConfusionMatrix.png)\

@@

::: {#fig-statisticalDecisionTree}
![](images/statisticalDecisionTree.png)\

@@

::: {#fig-statisticalDecisionTreeSummary}
![](images/statisticalDecisionTreeSummary.png)\

@@

::: {#fig-statisticalDecisionTreeRegression}
![](images/statisticalDecisionTreeRegression.png)\

@@

::: {#fig-statisticalDecisionTreeSummaryRegression}
![](images/statisticalDecisionTreeSummaryRegression.png)\

>>>>

::: {#fig-nhstConfusionMatrix}
![](images/nhstConfusionMatrix.png){fig-alt="A Two-by-Two Confusion Matrix for Null-Hypothesis Significance Testing."}

@@

::: {#fig-statisticalDecisionTree}
![](images/statisticalDecisionTree.png){fig-alt="A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R. & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including the addition of several statistical tests."}

@@

::: {#fig-statisticalDecisionTreeSummary}
![](images/statisticalDecisionTreeSummary.png){fig-alt="Summary of A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure."}

@@

::: {#fig-statisticalDecisionTreeRegression}
![](images/statisticalDecisionTreeRegression.png){fig-alt="A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure, Re-Formulated in a Regression Framework. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R. & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including re-formulating the tests in a regression framework."}

@@

::: {#fig-statisticalDecisionTreeSummaryRegression}
![](images/statisticalDecisionTreeSummaryRegression.png){fig-alt="Summary of A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure."}

### 2024-10-17 causal-inference.qmd
20241016 - figure alt text

::: {#fig-crossSectional}
![](images/Longitudinal-01.png){width=20%}\

@@

::: {#fig-laggedAssociation}
![](images/Longitudinal-02.png)\

@@

::: {#fig-laggedAssociationControlPriorLevels}
![](images/Longitudinal-03.png)\

@@

::: {#fig-crossLaggedPanelModel}
![](images/Longitudinal-04.png)\

@@

::: {#fig-simpsonParadox}
![](images/simpsonParadox.png){width=200%}\

>>>>

::: {#fig-crossSectional}
![](images/Longitudinal-01.png){width=20% fig-alt="Cross-Sectional Association. T1 = Timepoint 1. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

@@

::: {#fig-laggedAssociation}
![](images/Longitudinal-02.png){fig-alt="Lagged Association. T1 = Timepoint 1. T2 = Timepoint 2. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

@@

::: {#fig-laggedAssociationControlPriorLevels}
![](images/Longitudinal-03.png){fig-alt="Lagged Association, Controlling for Prior Levels of the Outcome. T1 = Timepoint 1. T2 = Timepoint 2. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

@@

::: {#fig-crossLaggedPanelModel}
![](images/Longitudinal-04.png){fig-alt="Lagged Association, Controlling for Prior Levels of the Outcome, Simultaneously Testing Both Directions Of Effect. T1 = Timepoint 1. T2 = Timepoint 2. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

@@

::: {#fig-simpsonParadox}
![](images/simpsonParadox.png){width=200% fig-alt="Example Where Failing to Control for a Variable (In This Case, Gender) Would Lead to False Inferences. In this example, the association between dosage and recovery probability is positive at the population level, but the association is negative among men and women separately. (Figure reprinted from @Kievit2013, Figure 1, p. 2. Kievit, R., Frankenhuis, W., Waldorp, L., & Borsboom, D. (2013). Simpson's paradox in psychological science: A practical guide. *Frontiers in Psychology*, *4*(513). https://doi.org/10.3389/fpsyg.2013.00513)"}

### 2024-10-17 cognitive-bias.qmd
20241016 - figure alt text

::: {#fig-prospectTheory}
![](images/prospectTheory.png)\

@@

::: {#fig-dunningKrueger1}
![](images/dunningKrueger_1.png)\

@@

::: {#fig-dunningKrueger2}
![](images/dunningKrueger_2.png)\

>>>>

::: {#fig-prospectTheory}
![](images/prospectTheory.png){fig-alt="Prospect Theory and Loss Aversion: People Tend to Weigh Losses More Heavily Than Gains. That is, the utility function is steeper in the loss (red) region than in the gain (blue) region. Adapted from <https://commons.wikimedia.org/wiki/File:Graphique_th%C3%A9orie_des_perspectives.svg>."}

@@

::: {#fig-dunningKrueger1}
![](images/dunningKrueger_1.png){fig-alt="Dunning–Krueger Effect: Confidence as a Function of Competence. People with low competency in a task tend to overestimate their ability. Adapted from <https://commons.wikimedia.org/wiki/File:Effet_Dunning-Kruger.svg>."}

@@

::: {#fig-dunningKrueger2}
![](images/dunningKrueger_2.png){fig-alt="Dunning–Krueger Effect: Perceived Performance as a Function of Actual Performance. People who perform poorly in a task tend to overestimate their performance. Adapted from <https://commons.wikimedia.org/wiki/File:Dunning-kruger_effect_-_percentile.svg>."}

### 2024-10-17 fantasy-football.qmd
20241016 - figure alt text

::: {#fig-footballFormation}
![](images/footballFormation.png)\

@@

::: {#fig-footballField}
![](images/footballField.png){width=50%}\

>>>>

::: {#fig-footballFormation}
![](images/footballFormation.png){fig-alt="An Example Football Formation for the Offense and Defense. The solid line indicates the line of scrimmage. The arrow indicates the direction the offense tries to advance the ball."}

@@

::: {#fig-footballField}
![](images/footballField.png){width=50% fig-alt="A Diagram of a Football Field. The yard markers depict the distance from the nearest end zone. The orange shaded area is called the "red zone", where chances of scoring points are highest. The original figure was modified to depict field goal posts. (Figure retrieved from <https://commons.wikimedia.org/wiki/File:American_football_field.svg>"}

### 2024-10-17 multiple-regression.qmd
20241016 - add alt-text to figures
20241016 - figure alt text

::: {#fig-regression}
![](images/regression.png)

@@

::: {#fig-regression}
![](images/multipleRegressionRSquared.png){width=50%}

@@

```{r}
#| label: fig-overfittingModel
#| fig-cap: "Over-fitting Model in Red Relative to the True Distribution of the Data in Blue. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| code-fold: true

@@

::: {#fig-regression}
![](images/multipleRegressionMulticollinearity.png){width=50%}

>>>>

::: {#fig-regression}
![](images/regression.png){fig-alt="A Regression Best-Fit Line."}

@@

::: {#fig-regression}
![](images/multipleRegressionRSquared.png){width=50% fig-alt="Conceptual Depiction of Proportion of Variance Explained ($R^2$) in an Outcome Variable ($Y$) by Multiple Predictors ($X1$ and $X2$) in Multiple Regression. The size of each circle represents the variable's variance. The proportion of variance in $Y$ that is explained by the predictors is depicted by the areas in orange. The dark orange space ($G$) is where multiple predictors explain overlapping variance in the outcome. Overlapping variance that is explained in the outcome ($G$) will not be recovered in the regression coefficients when both predictors are included in the regression model. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

@@

```{r}
#| label: fig-overfittingModel
#| fig-cap: "Over-fitting Model in Red Relative to the True Distribution of the Data in Blue. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| fig-alt: "Over-fitting Model in Red Relative to the True Distribution of the Data in Blue. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."
#| code-fold: true

@@

::: {#fig-regression}
![](images/multipleRegressionMulticollinearity.png){width=50% fig-alt="Conceptual Depiction of Multicollinearity in Multiple Regression. From @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

### 2024-10-17 research-methods.qmd
20241016 - render the figure caption as alt text
20241016 - figure alt text

::: {#fig-correlationAndCausation1}
![](images/correlationAndCausation_1.png)

@@

::: {#fig-correlationAndCausation2}
![](images/correlationAndCausation_2.png)

@@

::: {#fig-correlationAndCausation3}
![](images/correlationAndCausation_3.png)

@@

::: {#fig-correlationAndCausation4}
![](images/correlationAndCausation_4.png)

@@

::: {#fig-mediationModerationMnemonic}
![](images/mediationModerationMnemonic.png)

@@

::: {#fig-mediation}
![](images/mediation.png)

@@

::: {#fig-mediationExample}
![](images/mediationExample.png)

@@

::: {#fig-fullMediation}
![](images/mediation.png)

@@

::: {#fig-partialMediation}
![](images/mediationPartial.png)

@@

::: {#fig-multipleMediators}
![](images/mediationMultiple.png)

@@

::: {#fig-moderation}
![](images/moderation.png)

@@

::: {#fig-moderationExamplePathDiagram}
![](images/moderationExample1.png)

@@

::: {#fig-moderationExampleInteractionGraph}
![](images/moderationExample2.png)

@@

::: {#fig-reliabilityVsValidity}
![](images/reliabilityVsValidity.png)

>>>>

::: {#fig-correlationAndCausation1}
![](images/correlationAndCausation_1.png){fig-alt="Hypothesized Causal Effect Based on an Observed Association Between `X` and `Y`, Such That `X` Causes `Y`."}

@@

::: {#fig-correlationAndCausation2}
![](images/correlationAndCausation_2.png){fig-alt="Reverse (Opposite) Direction of Effect From the Hypothesized Effect, Where `Y` Causes `X`."}

@@

::: {#fig-correlationAndCausation3}
![](images/correlationAndCausation_3.png){fig-alt="Bidirectional Effect Between `X` and `Y`, such that `X` causes `Y` and `Y` causes `X`."}

@@

::: {#fig-correlationAndCausation4}
![](images/correlationAndCausation_4.png){fig-alt="Confounded Association Between `X` and `Y` due to a Common Cause, `Z`."}

@@

::: {#fig-mediationModerationMnemonic}
![](images/mediationModerationMnemonic.png){fig-alt="Mediation Versus Moderation Mnemonic."}

@@

::: {#fig-mediation}
![](images/mediation.png){fig-alt="Mediation."}

@@

::: {#fig-mediationExample}
![](images/mediationExample.png){fig-alt="Mediation Example."}

@@

::: {#fig-fullMediation}
![](images/mediation.png){fig-alt="Full Mediation."}

@@

::: {#fig-partialMediation}
![](images/mediationPartial.png){fig-alt="Partial Mediation."}

@@

::: {#fig-multipleMediators}
![](images/mediationMultiple.png){fig-alt="Multiple Mediators."}

@@

::: {#fig-moderation}
![](images/moderation.png){fig-alt="Moderation."}

@@

::: {#fig-moderationExamplePathDiagram}
![](images/moderationExample1.png){fig-alt="Moderation Example: Path Diagram."}

@@

::: {#fig-moderationExampleInteractionGraph}
![](images/moderationExample2.png){fig-alt="Moderation Example: Interaction Graph."}

@@

::: {#fig-reliabilityVsValidity}
![](images/reliabilityVsValidity.png){fig-alt="Reliability Versus Validity."}
